Summary of PM2.5 Nonattainment  Analysis

### 2020-11-12 Analysis Files/Paper_Analysis_327.Rmd
adding sensitivity analysis

```{r}
rm(list=ls())
set.seed(51)
# library(HEIfunctions)
library(maps)
library(PSAgraphics)
library(data.table)
library(randomForest)

@@

method = "RF"

@@

>>>>

```{r}
rm(list=ls())
set.seed(51)
# library(HEIfunctions)
source("mvspmod.R")
library(maps)
library(PSAgraphics)
library(data.table)
library(randomForest)

@@

# method = "RF"
method = "logit"

@@

## Sensitivity analysis
```{r, echo=FALSE}
library(sensitivitymult)
source("utility.R")

cast.1to1 <- cast.senm(dat, ms.1)

compute_FRT <- function(gamma) {
  FRT <- senm(y=cast.1to1$y, z=cast.1to1$z, mset=cast.1to1$mset, gamma=gamma, inner=0, trim=Inf)
  return(FRT$pval)
}

gammas <- seq(1, 3, 0.1)
pvals <- sapply(gammas, FUN = "compute_FRT")
cat("FRT for 1:1 ms. p-values:", pvals)
df <- data.frame(x = gammas, y = pvals)

ggplot(data=df, aes(x, y)) +
  geom_line() +
  geom_hline(yintercept = 0.05, color='coral') +
  xlab("Maximum deviation in odds of treatment assignment (Gamma)") +
  ylab("p-value from FRT") +
  theme_minimal()
```
